### 2014-03-14 docs/paper.tex
Better discussion of OSS.

Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to endpoint blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and endpoint-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.

@@

A technique known as OSS~\cite{oss} (for
``online scanning service'') resembles ours in certain ways. OSS bounces data
through third-party web services that are capable of making HTTP requests.
Even though such services can fetch a web page, they do not in general
preserve the contents of the page when it is returned to the requestor.
(A translation service, for example,
returns the page after translating it to another language.)
For this reason, OSS does not rely on being able to send downstream data in HTTP response bodies,
but rather requires the server to make a symmetric reflected HTTP request back to the client.
The main ways in which this work differs is that we are effectively using an OSS that we fully control:
we can ensure that reflected HTTP traffic is unmodified;
and we make the OSS hard to block by hosting it on an important network resource.

>>>>

Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to endpoint blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
The client must be able to receive a TCP connection; in particular it
may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and endpoint-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.

@@

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces data
through third-party web services that are capable of making HTTP requests.
For example, a censored client may ask a translation service to
translate a web page at \url{http://proxy.example.com/...}, where ``\url{...}''
stands for the data payload that the client wishes to send---data are embedded in the URL.
Simply by making the HTTP request, the service sends the client's message.
The client cannot rely on being able to receive the response to its message in an HTTP response,
because online scanning services do not in general
return unmodified the contents of the page they are ordered to retrieve.
The translation service, for example, returns the page in another language.
For this reason, the server sends a response message by making
another reflected HTTP request back to the client, through the same OSS or a different one.
The need for the client to receive a connection means that OSS has the same problem with NAT that flash proxy does.
The NAT aspect is the most important way in which our work improves on OSS.
App Engine is effectively an unblockable OSS that we fully control.
We can ensure that reflected HTTP bodies are unmodified, and therefore use them to carry traffic
without having to connect to the client.
